Topological approach to finding blackholes in directed networks

### 2019-12-07 blackholes/pavt/article.tex
Fix algo name

\begin{table}[]
\caption{Experimental results}
\label{tabular:tableresults}
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
Graph & Type & Algorithm & Blackholes & Time(s) & Algorithm & Blackholes & Time(s) \\
\hline
RMAT 04 & chinese & 1 & 0.00039521 & topsort & 1 & 0.000115912 \\
RMAT & 06 & chinese & 1 & 0.0040142 & topsort & 1 & 0.00034812 \\
RMAT & 08 & chinese & 1 & 0.0637587 & topsort & 1 & 0.00146486 \\
RMAT & 10 & chinese & 6 & 1200 & topsort & 10 & 0.00684045 \\
RMAT & 12 & chinese & 29 & 1200 & topsort & 971738 & 1200 \\
RMAT & 14 & chinese & 187 & 1200 & topsort & 735128 & 1200 \\
RMAT & 16 & chinese & 1192 & 1200 & topsort & 373705 & 1200 \\
RMAT & 18 & chinese & 5161 & 1200 & topsort & 10286 & 1200 \\
RMAT & 20 & chinese & 609 & 1200 & topsort & 48867 & 1200 \\
RMAT & 22 & chinese & 108 & 1200 & topsort & 0 & 1200 \\
SSCA2 & 04 & chinese & 16 & 0.255101 & topsort & 16 & 0.000189925 \\
SSCA2 & 06 & chinese & 11 & 1200 & topsort & 70 & 0.00121528 \\
SSCA2 & 08 & chinese & 42 & 1200 & topsort & 263314 & 1200 \\
SSCA2 & 10 & chinese & 85 & 1200 & topsort & 114411 & 1200 \\
SSCA2 & 12 & chinese & 343 & 1200 & topsort & 5870 & 1200 \\
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\caption{Experimental results. Part 2}
\label{tabular:tableresults2}
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
Graph & Type & Algorithm & Blackholes & Time(s) & Algorithm & Blackholes & Time(s) \\
SSCA2 & 14 & chinese & 1433 & 1200 & topsort & 323671 & 1200 \\
SSCA2 & 16 & chinese & 5829 & 1200 & topsort & 893376 & 1200 \\
SSCA2 & 18 & chinese & 23179 & 1200 & topsort & 224567 & 1200 \\
SSCA2 & 20 & chinese & 92347 & 1200 & topsort & 24199 & 1200 \\
SSCA2 & 22 & chinese & 370770 & 1200 & topsort & 0 & 1200 \\
UR & 04 & chinese & 1 & 0.000263955 & topsort & 1 & 0.000115029 \\
UR & 06 & chinese & 1 & 0.00222731 & topsort & 1 & 0.000331235 \\
UR & 08 & chinese & 1 & 0.0868632 & topsort & 1 & 0.00147483 \\
UR & 10 & chinese & 1 & 1.93527 & topsort & 1 & 0.00670724 \\
UR & 12 & chinese & 1 & 46.1463 & topsort & 1 & 0.034011 \\
UR & 14 & chinese & 1 & 1169.28 & topsort & 1 & 0.47257 \\
UR & 16 & chinese & 0 & 1200 & topsort & 1 & 3.05003 \\
UR & 18 & chinese & 0 & 1200 & topsort & 1 & 14.5788 \\
UR & 20 & chinese & 0 & 1200 & topsort & 1 & 67.7176 \\
UR & 22 & chinese & 0 & 1200 & topsort & 1 & 373.244 \\
\end{tabular}
\end{center}
\end{table}
\pagebreak

>>>>

\begin{table}[]
\caption{Experimental results}
\label{tabular:tableresults}
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
Graph & Type & Algorithm & Blackholes & Time(s) & Algorithm & Blackholes & Time(s) \\
\hline
RMAT 04 & iBlackhole & 1 & 0.00039521 & TopSort & 1 & 0.000115912 \\
RMAT & 06 & iBlackhole & 1 & 0.0040142 & TopSort & 1 & 0.00034812 \\
RMAT & 08 & iBlackhole & 1 & 0.0637587 & TopSort & 1 & 0.00146486 \\
RMAT & 10 & iBlackhole & 6 & 1200 & TopSort & 10 & 0.00684045 \\
RMAT & 12 & iBlackhole & 29 & 1200 & TopSort & 971738 & 1200 \\
RMAT & 14 & iBlackhole & 187 & 1200 & TopSort & 735128 & 1200 \\
RMAT & 16 & iBlackhole & 1192 & 1200 & TopSort & 373705 & 1200 \\
RMAT & 18 & iBlackhole & 5161 & 1200 & TopSort & 10286 & 1200 \\
RMAT & 20 & iBlackhole & 609 & 1200 & TopSort & 48867 & 1200 \\
RMAT & 22 & iBlackhole & 108 & 1200 & TopSort & 0 & 1200 \\
SSCA2 & 04 & iBlackhole & 16 & 0.255101 & TopSort & 16 & 0.000189925 \\
SSCA2 & 06 & iBlackhole & 11 & 1200 & TopSort & 70 & 0.00121528 \\
SSCA2 & 08 & iBlackhole & 42 & 1200 & TopSort & 263314 & 1200 \\
SSCA2 & 10 & iBlackhole & 85 & 1200 & TopSort & 114411 & 1200 \\
SSCA2 & 12 & iBlackhole & 343 & 1200 & TopSort & 5870 & 1200 \\
\end{tabular}
\end{center}
\end{table}

\begin{table}[]
\caption{Experimental results. Part 2}
\label{tabular:tableresults2}
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
Graph & Type & Algorithm & Blackholes & Time(s) & Algorithm & Blackholes & Time(s) \\
SSCA2 & 14 & iBlackhole & 1433 & 1200 & TopSort & 323671 & 1200 \\
SSCA2 & 16 & iBlackhole & 5829 & 1200 & TopSort & 893376 & 1200 \\
SSCA2 & 18 & iBlackhole & 23179 & 1200 & TopSort & 224567 & 1200 \\
SSCA2 & 20 & iBlackhole & 92347 & 1200 & TopSort & 24199 & 1200 \\
SSCA2 & 22 & iBlackhole & 370770 & 1200 & TopSort & 0 & 1200 \\
UR & 04 & iBlackhole & 1 & 0.000263955 & TopSort & 1 & 0.000115029 \\
UR & 06 & iBlackhole & 1 & 0.00222731 & TopSort & 1 & 0.000331235 \\
UR & 08 & iBlackhole & 1 & 0.0868632 & TopSort & 1 & 0.00147483 \\
UR & 10 & iBlackhole & 1 & 1.93527 & TopSort & 1 & 0.00670724 \\
UR & 12 & iBlackhole & 1 & 46.1463 & TopSort & 1 & 0.034011 \\
UR & 14 & iBlackhole & 1 & 1169.28 & TopSort & 1 & 0.47257 \\
UR & 16 & iBlackhole & 0 & 1200 & TopSort & 1 & 3.05003 \\
UR & 18 & iBlackhole & 0 & 1200 & TopSort & 1 & 14.5788 \\
UR & 20 & iBlackhole & 0 & 1200 & TopSort & 1 & 67.7176 \\
UR & 22 & iBlackhole & 0 & 1200 & TopSort & 1 & 373.244 \\
\end{tabular}
\end{center}
\end{table}
\pagebreak
